Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-13 paper.tex
Terminating the revision to the intro
Refs #45

In Spain, the process of releasing a book goes like this: the
publisher decides, based on past experience, how many books to
print. These books are distributed to points of sale, but also given
out to reviewers and literary magazines, the number of these will
depend on how many you have printed. Books then go, in some cases, to
the {\em novelty} table, that is, prominently displayed in the
bookstore, shown in the window, or highlighted using props or other
kind of advertisement. Books stay for sale for as long as the
publisher or the store want until the bookseller decides to return it
to the publisher or just, in some cases, move it away from shelves to
storage. Books returned to the publisher are pulped, sold back or
given to the author or distributed in second-hand channels such as
book stalls or second-hand bookstores. If the print run has been fully
distributed and there are more requests from bookstores, on the other
hand, a new print run is made and distributed to bookstores. 
Even if the process has changed
in the last few years since Amazon started to sell in Spain, which
actually happened {\em after} the data used for this paper was
collected, it roughly stays the same. Other countries will have a
similar model, although scale will be different.

Our intention in this paper is to find out the main factor influencing
sales in order to give a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a  company that sells
software for publishers, we analyse it by means of different data
mining methods and create predictive models that can be mainly used as
decision-aid tools for book publishers. With these models, publishers
will be able to 
combine their expert knowledge about the market with the created
forecasting models in order to get a reliable estimation of book
sales, and, based on it, act upon it to maximize the books sold for a
particular print run.

In the research published in this paper, the problem 
of predicting total sales in order to print the right amount of books
%of how many units should be printed  when a new book is published 
is faced using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data and applied their knowledge using external variables to compute correct estimations (predictions); for instance, they can decide increasing or decreasing the sales forecast based on season or sales period.
Nevertheless, just carrying out the analysis and forecasting process as a human expert may lead to imprecise predictions, and they may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

With this issue in mind, in this paper we firstly present an analysis on the aforementioned real dataset, by means of data mining and visualisation techniques. Then, a feature selection process is conducted using three different methods, in order to find out what are the relevant variables describing a book in the prediction (or regression) procedure. After this, a forecasting stage is performed applying a set of regression algorithms to the different datasets, also considering a different number of variables.
The value of this methodology is contrasted considering four different publishing companies being representative as top sellers, mid-range sellers, the most varied, and one which sells a medium amount of different books.

>>>>

In Spain, the process of releasing a book goes like this: the
publisher decides, based on past experience, how many books to
print. These books are distributed to points of sale, but also given
out to reviewers and literary magazines; the number of these will
depend on how many you have printed. In bookstores books  go, in some cases, to
the {\em novelty} table, that is, they are prominently displayed, shown in the window, or highlighted using props or other 
kind of advertisement. From these displays they then move to shelves
or, in some cases and eventually, to storage. Books stay for sale in the store as long as the
publisher or the store want or until the bookseller decides to return it
to the publisher. Books returned to the publisher are pulped, sold back or
given to the author or distributed in used-books channels such as
book stalls or second-hand bookstores. If the print run has been fully
distributed and there are more requests from bookstores, on the other
hand, a new print run is made and distributed to bookstores. 
Even if the process has changed slightly 
in the last few years since Amazon started to sell in Spain, in the
sense that many books are sold through this new channel and do not
undergo the cycle novelty table-shelf-storage-back to publisher, which
actually happened {\em after} the data used for this paper was
collected, it roughly stays the same. Other countries will have a
similar model, although scale will be different.

Our intention in this paper is to find out the main factors influencing
sales in order to create a tool that the publisher can use to decide how
many books should be printed, as well as how to leverage these printed
copies to maximize sales using the decision variables under his
control. That is why, using data obtained from a  company that sells
software for publishers, we analyse it by means of different data
mining methods and create predictive models that can be mainly used as
decision-aid tools for book publishers. With these models, publishers
will be able to 
combine their expert knowledge about the market with the created
forecasting models in order to get a reliable estimation of book
sales, and, based on it, act upon it to maximize the books sold for a
particular print run. Our main contribution is, thus, to develop a
methodology to process book sales data in order to first find out
relevant variables and then use these variables to process data so
that the publisher, using them, can estimate sales and from them order
a specific print run, instead of standard ones, which are around 300
copies for standard books and around 5000 for those that are
considered, in advance, {\em best sellers}.

In the research published in this paper, the problem 
of predicting total sales in order to print the right amount of books
%of how many units should be printed  when a new book is published 
is approached using real data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}}. It provides management systems and services for bookshops, publishers, and distributors. 
Usually, the company's expert sales managers analysed historical data
and applied their knowledge on external variables to compute correct
estimations (predictions); for instance, they can decide increasing or
decreasing the sales forecast based on season or sales period. 
Nevertheless, just carrying out the analysis and forecasting process
as a human expert may lead to imprecise predictions, and they may not
take all the variables into account.  
In addition, the process might be tedious, especially when the amount
of data is quite large. Moreover, different experts can reach different
predictions from the same dataset \cite{Sanders1994}.

@@

With this issue in mind, in this paper we firstly present an analysis
on the aforementioned real dataset, by means of data mining and
visualisation techniques. Then, a feature selection process is
conducted using three different methods, in order to find out what are
the relevant variables describing a book in the prediction (or
regression) procedure. After this, a forecasting stage is performed
applying a set of regression algorithms to the different datasets,
also considering a different number of variables. 
The value of this methodology is contrasted considering four different
publishing companies being representative as top sellers, mid-range
sellers, the most varied, and one which sells a medium amount of
different books. From this, we draw insight on what are the important
factors when selling a book and some rule of thumbs extracted from the
prediction methods.
